Automated Formal Synthesis of Digital Controllers for State-Space Physical Plants

### 2017-01-25 cav2017/cav2017.tex
wordings

\begin{enumerate}
%
\item In this paper we extend the problem of digital control synthesis 
  from a transfer function representation into a state-space representation. 
  Such representation allows to study the  input-to-state dynamics, while 
  transfer functions represents only input-output relations and cannot be 
  enough to ensure deeper properties, e.g., the safety property.
%
\item We proposes a synthesis of state-feedback controllers that guarantees 
  safety properties, that is only  possible in state-space representation. 
  In addition to the already existing stability conditions which is a much 
  harder problem.
%
\item We develop two approaches: the first, naive, one relies on
  explicit unfolding of the system's dynamics up to the completeness
  threshold, whilst the second one is abstraction-based and leverages
  the concepts of abstraction refinement and acceleration to increase 
  speed whilst retaining soundness. Both approaches provide sound
  synthesis of state-feedback systems considering the various
  error sources in the implementation of the control algorithm and in the
  computational modeling of plant dynamics.
%
\item We develop a model for different sources quantization and their
  effect on the state-space progression, for which we find safe bounds
  that ensure the safety of our controllers in a hybrid
  continuous-digital domain.
%
\end{enumerate}

>>>>

\begin{enumerate}
%
\item  We give a novel synthesis algorithm for generating
  state-feedback controllers that are provably stable and in addition
  guaranteee a given safety property. Existing methods for controller
  synthesis rely on transfer function representations, which are
  insufficient to prove safety requirements.
%
\item We give two algorithms: the first, naive one, relies on
  an unfolding of the system's dynamics up to a completeness threshold,
  while the second one is abstraction-based and leverages abstraction
  refinement and acceleration to improve the scalability of the analysis
  while retaining soundness.  Both approaches provide sound synthesis of
  state-feedback systems and consider the various sources of imprecision in
  the implementation of the control algorithm and in the computational
  modeling of plant dynamics.
%
\item We develop a model for different sources of quantization errors and
  their effect on reachability properties.  We give bounds that ensure the
  safety of our controllers in a hybrid continuous-digital domain.
%
\end{enumerate}
